---
title: "Take-home Exercise 4"
description: |
  Putting Visual Analytics into Practical Use
author:
  - name: Zhou Yiou 
    url: https://example.com/zhouyiou
    affiliation: MITB SMU
    affiliation_url: https://example.com/spacelysprokets
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T,fig.dim=c(20,15))
```

##  1.0 About the task

This [take-home exercise](https://isss608-ay2021-22t2.netlify.app/th_ex/th_ex04) requires to apply appropriate data visualization techniques learned in Lesson 6 to accomplish the following tasks:

1. Script stock prices of top 40 companies in Singapore by market capitalisation between 1st January 2020 - 31st December 2021 by using *tidyquant* R package.

2. Using horizon graph to plot historical stock prices by the top 40 companies by market capitalisation.


##  2.0 Installing and loading the required libraries

In this exercise, tidyquant, tidyverse, ggplot2, dyplyr, and Knitr will be used.

  + `readr` for importing csv into R.
  + `tidyquant` to return objects in the tidy ‘tibble’ format and use quantitative functions together with the tidyverse functions.
  + `knitr` for building static html table.
  + `ggHoriPlot` for building horizon plots in ggplot2.

```{r echo=T}
packages = c('tidyverse', 'tidyquant', 'ggplot2','dplyr','tidyr','ggthemes','ggHoriPlot',
             'knitr')
for(p in packages){
  if(!require(p,character.only = T)){
    install.packages(p)
  }
  library(p,character.only = T)
}
```

##  3.0 data wrangling

Script data from [top 40 companies in Singapore by market capitalisation](https://companiesmarketcap.com/singapore/largest-companies-in-singapore-by-market-cap/)
  
Reference: [scraping of fiancial dataset](https://giniceseah.netlify.app/posts/2021-06-18-scraping-of-financial-dataset/#tidyquant-package)

#### Import the data:

```{r echo=T}
Companies<-read.csv('data/companiesmarketcap.csv')
```

####Prepare the data:

Only the list of symbols was retained for the subsequent use. `slice_max()` is used to get the top 40 stocks in SGX by *marketcap*.

```{r}
top40<-Companies%>%
  slice_max(`marketcap`,n=40)%>%
  select(Symbol,Name)
```
#### Script data from Yahoo Finance:

The following code is used to manipulate and select the stock symbols within 1 January 2020 to 31 December 2021  from Yahoo Finance as required. The data was returned in daily intervals. 
`tq_get()` function in tidyquant R packages is used to retrieve date, volume, opening, highest, lowest, closing, and adjusted price.

```{r echo=TRUE, message=FALSE, warning=FALSE}
from_date = "2020-01-01"
to_date = "2021-12-31"
period_type = "days"  # "days"/ "weeks"/ "months"/ "years"

stock_data_daily<-top40 %>%  
  tq_get(get = "stock.prices",
         from = from_date,
         to = to_date) %>%
  group_by(Symbol,Name)%>%
  select(Symbol,Name,date,close)%>%
  tq_transmute(select = NULL, 
               mutate_fun = to.period, 
               period  = period_type)
rmarkdown::paged_table(stock_data_daily)
```

## 4.0 Data Visualization

Build the horizon plots in ggplot2 using geom_horizon():

```{r echo=T}
stock_data_daily %>% ggplot() +
  geom_horizon(aes(date, close))+
  scale_fill_hcl(palette = 'RdBu', reverse = T) + #set the color palette
  facet_grid(Name~.) +
  theme_few() +
  theme(
    panel.spacing.y=unit(0, "lines"),
    strip.text.y = element_text(size = 7, angle = 0, hjust = 0),
    axis.text.y = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks.y = element_blank(),
    panel.border = element_blank()
    ) +
  scale_x_date(expand=c(0,0), 
               date_breaks = "1 month", 
               date_labels = "%b%Y") +
  xlab('Date') +
  ggtitle('Close price of SGX top 40 by marketcap', 
          'from 1/1/2020 to 31/12/2021')
```

Adjust the size of fond, set the x-axis interval to 3 months. 

```{r}
stock_data_daily %>% ggplot() +
  geom_horizon(aes(date, close),origin = "median",horizonscale = 6)+
  scale_fill_hcl(palette = 'RdBu', reverse = T) + #set the color palette
  facet_grid(Name~.) +
  theme_few() +
  theme(
    panel.spacing.y=unit(0, "lines"),
    strip.text.y = element_text(size = 16, angle = 0, hjust = 0),
    axis.text.x = element_text(size = 20),
    axis.text.y = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks.y = element_blank(),
    panel.border = element_blank(), 
    axis.title=element_text(size=20,face="bold"),
    plot.title = element_text(size=28, face = "bold"),
    plot.subtitle = element_text(size=20, face = "bold")
    ) +
  scale_x_date(expand=c(0,0), 
               date_breaks = "3 month", 
               date_labels = "%b") +
  xlab('Date') +
  ggtitle('Close price of SGX top 40 by marketcap', 
          'from 1/1/2020 to 31/12/2021')
```

