---
title: "Take-home Exercise 3"
description: |
  Putting Visual Analytics into Practical Use
author:
  - name: Zhou Yiou 
    url: https://example.com/zhouyiou
    affiliation: MITB SMU
    affiliation_url: https://example.com/spacelysprokets
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

##  1.0 About the task

This [take-home exercise](https://isss608-ay2021-22t2.netlify.app/th_ex/th_ex03) requires to apply appropriate data visualization techniques learned in Lesson 4 to accomplish the following task:  

Create a data visualisation to provide an unbiased comparison of order returned by state. 

For this task, Superstore-2021.xls should be used and the chart applied here are from [Hands-On Exercise 4: Building Funnel Plot with R](https://isss608-ay2021-22t2.netlify.app/hands-on_ex/hands-on_ex04/hands-on_ex04-funnelplot)

##  2.0 Installing and loading the required libraries

In this exercise, tidyverse, FunnelPlotR, plotly and Knitr will be used.

  + readr for importing csv into R.
  + FunnelPlotR for creating funnel plot.
  + ggplot2 for creating funnel plot manually.
  + knitr for building static html table.
  + plotly for creating interactive funnel plot.

```{r echo=T}
packages = c('tidyverse', 'FunnelPlotR', 'plotly','dplyr',
             'knitr','readxl')
for(p in packages){
  if(!require(p,character.only = T)){
    install.packages(p)
  }
  library(p,character.only = T)
}
```

##  3.0 data wrangling

Importing data

```{r echo=TRUE, message=FALSE, warning=FALSE}
orders <- read_xls("data/Superstore-2021.xls",
                  sheet = "Orders")
returns <- read_xls("data/Superstore-2021.xls",
                  sheet = "Returns")
```

Join orders table and returns table

```{r echo=T}
store <- left_join(returns, orders,
                        by = c('Order ID' = 'Order ID'))%>%
mutate_if(is.character,as.factor)
glimpse(store)
levels(store$Returned)
```

Count the number of return by state.

```{r echo=T}
sr <- store %>%
  group_by(State)%>%
  summarise('Returned'=n())%>%
  ungroup()
sr
```
count the number of orders by the state.

```{r}
so <- orders %>%
  group_by(State)%>%
  summarise('Order ID'=n())%>%
  ungroup()
so
```

join two dataframe

```{r}
ss <- left_join(so,sr,
                by = c('State' = 'State'))%>%
  mutate_if()
ss
```

##  4.0 FunnelPlotR methods

FunnelPlotR package uses ggplot to generate funnel plots. It requires a numerator (events of interest), denominator (population to be considered) and group. The key arguments selected for customisation are:

+ limit: plot limits (95 or 99).
+ label_outliers: to label outliers (true or false).
+ Poisson_limits: to add Poisson limits to the plot.
+ OD_adjust: to add overdispersed limits to the plot.
+ xrange and yrange: to specify the range to display for axes, acts like a zoom function.
+ Other aesthetic components such as graph title, axis labels etc.

### 4.1 FunnelPlotR methods: The basic plot

The code chunk below plots a funnel plot.

```{r echo=T}
fp<-funnel_plot(
  numerator = ss$Returned,
  denominator = ss$`Order ID`,
  group = ss$State
)
fp
```

### 4.2 FunnelPlotR methods: Makeover 1
```{r}
fp1<- funnel_plot(
  numerator = ss$Returned,
  denominator = ss$`Order ID`,
  group = ss$State,
  data_type = "SR",     
  xrange = c(0, 2500),  
  yrange = c(-0.1, 1.2)   
)
fp1
```
### 4.3 FunnelPlotR methods: Makeover 2
The code chunk below plots a funnel plot.

```{r}
fp2<- funnel_plot(
  numerator = ss$Returned,
  denominator = ss$`Order ID`,
  group = ss$State,
  data_type = "SR",     
  xrange = c(0, 2500),  
  yrange = c(0, 1.1),  
  label = NA,
  title = "Number of returned orders by total number of orders",      
  x_label = "Totoal number of orders",
  y_label = "Return rate" 
)
fp2
```








